Randomized trace estimation for parameter-dependent matrices applied to spectral density approximation

### 2024-07-07 paper/re-pro-badge.tex

This document, along with all included plots and tables, was generated from commit \href{https://github.com/FMatti/Rand-TRACE/tree/6f952d3}{6f952d3} at \url{https://github.com/FMatti/Rand-TRACE} on 2024-07-05 at 12:56:53 UTC.

>>>>

This document, along with all included plots and tables, was generated from commit \href{https://github.com/FMatti/Rand-TRACE/tree/ce5dd53}{ce5dd53} at \url{https://github.com/FMatti/Rand-TRACE} on 2024-07-07 at 11:46:28 UTC.
